NYC Spatial Models - Comparison of Spatial Models With and Without Twitter Data

### 2018-11-02 NYC_Twitter_SDM_models - Copy.Rmd
Look for missingness in tracts and parks datasets

```{r setup, echo=FALSE, message=FALSE, warning=FALSE}
library(geojsonio)
library(tidyverse)
library(maptools)
library(rgdal)
library(rgeos)
library(spdep)
library(texreg)
library(leaflet)
```

```{r read_tracts, echo=FALSE}
tracts <- geojson_read("nyc_tracts.geojson", what = "sp")
#plot(tracts)
```

```{r read_parks, echo=FALSE}
parks <- geojson_read("nyc_parks.geojson", what = "sp")
#plot(parks)
```

```{r show_data, echo=FALSE}
tracts@data <- tbl_df(tracts@data) %>%
  select(GEOID, OBESITY, Park_Percent, Phys_Act, MENTAL, Income1, Income2, Income3, Income4, Income5, Income6, Income7, Income8, Income9, Income10, Pop_Density, FulltimeWork, CollegeDeg, Pct0to17, Pct18to29, Pct30to64, Pct65plus, Single_Percent, PctWhite, PctBlack, PctNative, PctAsian, PctPacific, PctOther, PctHispanic) %>%
    mutate_each(funs(ifelse(is.na(.), 0, .)), Park_Percent)

@@

tracts@data
#parks@data
```

>>>>

This document contains the model estimation and impacts results for the paper.

```{r setup, echo=FALSE, message=FALSE, warning=FALSE}
library(geojsonio)
library(tidyverse)
library(maptools)
library(rgdal)
library(rgeos)
library(spdep)
library(texreg)
library(leaflet)
library(sf)
```

Nico cleaned the tracts dataset into a geoJSON file stored in the repository. We
should read it in twice because the sf library is better for visualization but
spdep still requires sp objects for now.

```{r read_tracts}
tracts <- geojson_read("nyc_tracts.geojson", what = "sp")
tracts_sf <- st_read("nyc_tracts.geojson", quiet = TRUE) %>%
  st_transform(4326)
```

## Complete Cases
We noticed that our models had different numbers of observations / degrees of 
freedom. Obviously we need to have comparable econometric models. The first thing
we want to look for is missingness in the tracts variables, and which tracts
are missing those variables. The map below shows the tracts that are missing
this information.

```{r tracts_with_missing}
# identify complete cases
complete_tracts_index <- tracts_sf %>%
  st_set_geometry(NULL) %>%
  tbl_df() %>%
  complete.cases()

# make a map of 
leaflet( tracts_sf[!complete_tracts_index, ]) %>%
  addProviderTiles(providers$OpenStreetMap.Mapnik) %>% 
  addPolygons(label = ~ as.character(GEOID))
```

These tracts seem to fall into two basic categories:

  - Tracts outside of New York City that were clipped into the shape layer 
  and remain as edge remnants. It is generally better to select by FIPS code rather
  than geometric operations, but we can just discard these at this point and
  they will not affect anything.

  - Tracts that are completely occupied by parks, airports, or other pieces
  of non-residential infrastructure.

The exceptions to this appear to be 3606100940 and 36061010200 in Midtown between
5th Avenue and Park Avenue. Greg will assume for this analysis that these are 
entirely commercial tracts and therefore have no residents, but Nico needs to 
verify these.

```{r complete_cases}
tracts <- tracts[complete_tracts_index, ]
```

The parks data seems relatively complete, with the exception of a few variables
that are missing everywhere. But we'll ignore this for now.

```{r read_parks, echo=FALSE}
parks <- geojson_read("nyc_parks.geojson", what = "sp")
parks_sf <- st_read("nyc_parks.geojson") %>%
  st_transform(4326)
#plot(parks)
```

```{r show_data, echo=FALSE}
tracts@data <- tbl_df(tracts@data) %>%
  select(
    GEOID, OBESITY, Park_Percent, Phys_Act, MENTAL, 
    Income1, Income2, Income3, Income4, Income5, Income6, 
    Income7, Income8, Income9, Income10, Pop_Density, 
    FulltimeWork, CollegeDeg, Pct0to17, Pct18to29, Pct30to64, Pct65plus, 
    Single_Percent, PctWhite, PctBlack, PctNative, PctAsian, PctPacific,
    PctOther, PctHispanic
  )

@@

tracts@data
parks@data
```
